Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
so close

\section{Privacy Controls}

One of the major concerns with storage of patient data is privacy. Indeed, there is also potentially
legal requirements on storing personal health data, depending on the nature of the data being
stored.

However, it is important that control of data be sufficiently granular so that patients can choose
to sure it with clinicians, and that clinicians can refer to it in their notes in the patient's health
record.

\section{Conclusion}

By augmenting data from personal health sensors with EHRs, both patients and clinicians
can gain insight into the lifestyle and typical activities of a patient. Challenges in implementation
of such a system do exist, but through the use of domain ontologies and peer-to-peer
sharing...

@@

Nigel Shadbolt (FBCS FREng) is Professor of Artificial Intelligence and Head of the Web and Internet Science Group, University of Southampton. He is the Chairman and Co-Founder of the Open Data Institute, Director of the Web Science Trust, and of the Web Foundation.  He and Sir Tim Berners-Lee were appointented as Information Advisors to the UK Government, leading to \url{data.gov.uk}. He is a member of the Public Sector Transparency Board, and Chair of the UK Government's midata programme.

\section{Key Technology: WebBox}

WebBox is...

@@

This work is supported under SOCIAM: The Theory and Practice of Social Machines.  The SOCIAM Project is funded by the UK Engineering and Physical Research Council (ESPRC) under grant number EP/J017728/1 and comprises the Universities of Southampton, Oxford and Edinburgh.

>>>>

%% \section{Privacy Controls}

%% One of the major concerns with storage of patient data is privacy. Indeed, there is also potentially
%% legal requirements on storing personal health data, depending on the nature of the data being
%% stored.

%% However, it is important that control of data be sufficiently granular so that patients can choose
%% to sure it with clinicians, and that clinicians can refer to it in their notes in the patient's health
%% record.

%% \section{Conclusion}

%% By augmenting data from personal health sensors with EHRs, both patients and clinicians
%% can gain insight into the lifestyle and typical activities of a patient. Challenges in implementation
%% of such a system do exist, but through the use of domain ontologies and peer-to-peer
%% sharing...

@@

Nigel Shadbolt (FBCS FREng) is Professor of Artificial Intelligence and Head of the Web and Internet Science Group, University of Southampton. He is the Chairman and Co-Founder of the Open Data Institute, Director of the Web Science Trust, and the Web Foundation.  He and Sir Tim Berners-Lee were Information Advisors to the UK Government, which led to \url{data.gov.uk}. He is a member of the Public Sector Transparency Board, and Chair of the UK Government's midata programme.

%% \section{Key Technology: WebBox}

%% WebBox is...

@@

This work is supported by the SOCIAM Project (EPSRC grant EP/J017728/1).
